\documentclass[10pt]{article}
% \def\StudentVersion{}
\usepackage{../../common}
\makeatletter

\def\LecStr{Alexander Rush}
\def\LecNum{1}
\def\LecTitle{Lectures Notes on Search}
\def\LecDate{}


\begin{document}
\MakeScribeTop{}

\section{Board 1}

Isabel

\section{Board 2}

\url{http://bits.blogs.nytimes.com/2015/04/13/ibm-creates-watson-health-to-analyze-medical-data/}

\section{Board 3}

\url{http://www.nytimes.com/2015/09/25/technology/ibms-ai-system-watson-to-get-new-west-coast-home.html?ref=business}

\begin{itemize}
\item Speech,
\item Image
\item Sentiment Analysis
\end{itemize}

\section{Board 4}

\url{http://www.nytimes.com/interactive/2010/06/16/magazine/watson-trivia-game.html?ref=science}

\section{Board 5}

\url{https://www.youtube.com/watch?v=P0Obm0DBvwI}

\section{Board 6}

Vocabulary

Evidence Based Medicine: 

Forward Reasoning: From Data to Conclusion through rules.

Mixed Initiative Dialog: Party can refine response. 

Open-Domain Question Answering: Question come from a large-scope of backgrounds ( constrast with flight planning).

Electronic Medical Records 

Evidence-based Medicine ``aim to apply the best available evidence gained from the scientific method'' Randomized control trials over case studies. 

Hypothesis generation;

abduction: collect evidence for hypothesis. (as opposed to proving. 

differential diagnosis: ddx. Many diseases many have the same symptoms how can we distinguish which one is correct.

provenence: tracing which factors lead to an outcome 

metacognitive errors: errors reasoning, mistakes in the reasoning process 

named-entity and relation extraction: 

ISABEL

discriminativeness: how well new information distinguishes hypotheses

Content adaptation: tuning the hypothesis collection tools
Training Adaptation:  Collecting training data, and rating its relevence
Functional Adaptation: adjusting tools to work with the domain itself

Information retrieval: search 

UMLS: show

structured versus unstructured text: UMLS versus mimic.
\end{document}

